\begin{thebibliography}{9}
\bibitem{Vehent} 
Julien Vehent, Forefox Services Security Lead at Mozilla. 
\textit{Test Driven Security in Coninouos Integration}. 
Enigma, January 30, 2017.
 
\bibitem{Zampetti} 
Fiorella Zampetti, Simone Scalabrino, Rocco Oliveto, Gerado Canfora, Massimiliano Di Penta. 
\textit{How Open Source Projects use Static Code Analysis Tools in Continuous Integration Pipelines}
2017 IEEE/ACM 14th International Conference on Mining Software Repositories (MSR).
 
\bibitem{spaceb0x} 
Exploiting Continous Integration (CI) and Automated Build Systems,
\\\texttt{https://media.defcon.org/DEF\%20CON\%2025/DEF\%20CON\%2025\%20presentations/DEFCON-25-spaceB0x-Exploiting-Continuous-Integration-UPDATED.pdf}
DEFCon 25

\bibitem{Hilton} 
Michael Hilton, Timothy Tunnell, Kai Huang, Darki Marinov, Danny Dig. 
\textit{Usage, Costs, and Benefits of Continuous Integration in Open-Source Projects}
TODO

\bibitem{Bass} 
Len Bass, Ralph Holz, Paul Rimba, An Binh Tran, Liming Zhu. 
\textit{Securing a Deployment Pipeline}
2015 IEEE/ACM 3rd International Workshop on Release Engineering.

\bibitem{Holck}
Jesper Holck, Niels Jørgensen.
\textit{Continuous Integration and Quality Assurance: a case study of two open source projects}
2017 IEEE/ACM 14th International Conference on Mining Software Repositories (MSR).
TODO

\bibitem{Case}
Andrew Case, Arghya Kusum Das, Seung-Jong Park, J. (Ram) Ramanujam, Golden G. Richard III.
\textit{Gaslight: A comprehensive fuzzing architecture for memory forensics
frameworks}
DFRWS 2017 USA d Proceedings of the Seventeenth Annual DFRWS USA

\end{thebibliography}
